Approximating the Number of COVID-19 Infections in the United States Across 2021

### 2023-07-10 reports/county_figures.Rmd
update county figures

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE,cache=FALSE, fig.width=10, fig.height=7)

@@

ggsave(here('figures/testing_rate_ratio-county.pdf'), width=11,height=7, dpi=400)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE,cache=TRUE, fig.width=10, fig.height=7)

@@

ggsave(here('figures/testing-rate-ratio-county.pdf'), width=11,height=7, dpi=400)

### 2023-07-10 writing/manuscript.Rmd
update county figures

For simplicity, at the state-level we focus on the implementation that does not vary by state or date. This also allows us to consider the entirety of 2021, since survey data is only available for dates after March 20, 2021. A full comparison of implementations is included in Supplementary Figure covidestim-concordance-state.

@@

include_graphics(here('figures/testing_rate_ratio-county.pdf'))

@@

county_coverage %>%
  bind_rows(state_coverage) %>%
  group_by(`Geographic Scale`) %>%
  arrange(desc(`Percent Contained in Interval`),
          .by_group=TRUE) %>%
  ungroup() %>%
  select(-`Geographic Scale`) %>%
  kbl(caption = "\\label{table:coverage}Coverage of Covidestim Medians at the County and State Levels",
      booktabs=TRUE,  
      escape=FALSE,
      digits=3) %>%
  kable_styling(latex_options=c("scale_down","HOLD_position"))  %>%
  group_rows(start_row=1, end_row =4, group_label= "County", 
             latex_gap_space = "0.7em",
             hline_after = TRUE) %>%
  group_rows(start_row=5, end_row =8, group_label= "State",
             latex_gap_space = "0.7em",
             hline_after = TRUE) %>%
  row_spec(1:(row_num-1),  hline_after = TRUE, 
           extra_css = "border-bottom: 1px solid;") %>%
  row_spec(0, font_size=11, bold=TRUE) %>%
  footnote(general = "The percent of simulation intervals where the Covidestim median falls below, within, or above the interval, when considering all simulation intervals for that implementation and geographic scale.", general_title ="", footnote_as_chunk=TRUE, threeparttable=TRUE)

@@

@@

>>>>

For simplicity, at the state-level we focus on the implementation where the priors do not vary by state or date. This also allows us to consider the entirety of 2021, since survey data is only available for dates after March 20, 2021. A full comparison of implementations is included in Supplementary Figure covidestim-concordance-state.

@@

include_graphics(here('figures/testing-rate-ratio-county.pdf'))

@@

county_coverage %>%
  bind_rows(state_coverage) %>%
  group_by(`Geographic Scale`) %>%
  arrange(desc(`Percent Contained in Interval`),
          .by_group=TRUE) %>%
  ungroup() %>%
  select(-`Geographic Scale`) %>%
  kbl(caption = "\\label{table:coverage}Coverage of Covidestim Medians at the County and State Levels",
      booktabs=TRUE,  
      escape=FALSE,
      digits=3) %>%
  kable_styling(latex_options=c("scale_down","HOLD_position"))  %>%
  group_rows(start_row=1, end_row =4, group_label= "County", 
             latex_gap_space = "0.7em",
             hline_after = TRUE) %>%
  group_rows(start_row=5, end_row =8, group_label= "State",
             latex_gap_space = "0.7em",
             hline_after = TRUE) %>%
  row_spec(1:(row_num-1),  hline_after = TRUE, 
           extra_css = "border-bottom: 1px solid;") %>%
  row_spec(0, font_size=11, bold=TRUE) %>%
  footnote(general = paste0("The percent of simulation intervals where the Covidestim median falls below, within, or above the interval,",
  "when considering all simulation intervals for that implementation and geographic scale.",
  "Implementations are ordered from those with the highest proportion of Covidestim medians contained in the interval, to the lowest."),
  general_title ="", footnote_as_chunk=TRUE, threeparttable=TRUE)

@@

#### $\alpha$

#### $\beta$

#### $\Pr(S_1| \text{untested})$

@@

\vspace{4 mm}
